Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-10-25 peakcharacterization_manuscript.Rmd
discuss normalization results and what we should see

### Model of M/Z Standard Deviation

**do we use this anywhere**?? Because if not, maybe we shouldn't bother including it.

@@

>>>>

### Frequency Standard Deviation Filtering

High-peak-density artifacts [Mitchell et al., 2018] present as singular peaks with higher than expected frequency standard deviations calculated from the scan-to-scan frequency peak locations. Outliers are removed by examining the distribution of peak frequency SDs across the entire spectrum.

@@

Due to differences in how many ions are captured in the trap, the peak intensities in each scan vary slightly.
There are two issues with these peak intensities across scans: 1 - Some peak intensities correlate with the scan; 2 - Some peak intensities are correlated with M/Z / frequency.
The solution to **1** is to do a two pass normalization, detect the correlated peak intensities, remove them, and then calculate normalization factors again.
Figure XA shows that some peaks will be correlated with scan number.
The solution to peak intensities correlated with M/Z appears to be tied to their intensities, as shown in Figure XB.
The highlighted peaks in Figure XB are those with an intensity greater than 0.7, and are **not** correlated with M/Z.
If *all* peaks are used for normalization, a very different set of normalization factors will be generated than by using only the *most intense* peaks, as shown in Figure XC.

```{r normalization_data}
# figure showing peak intensity correlation with M/Z, intensity varying with M/Z, changes in normalization using all vs most intense
```
